An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-07-08 jmiv.tex
fatigue

We do not use similarity terms in this section, thus we postpone the
definition of such terms until the description of how DCE can be used
in an image segmentation framework.

@@

In figure \ref{fig:m1-square-flow} we see some results for the DCE
algorithm with $m=1$. We observe a global movement towards roundness,
but with several artifacts. We minimize the effects of a jaggy
boundary by setting $\alpha > 0$. Nonetheless, a higher estimation
ball radius creates unstable shapes. In fact, the estimator is very
sensitive in regions of low squared curvature, and it is precisely in
those regions that spurious pixels are created.

@@

\subsection{A more stable model.}
In the previous section we noticed that the algorithm produces shapes
with many artifacts due to the small uncertainties of the estimator
along regions of low squared curvature. We argue that, evaluating the
estimation ball along farther ring sets we avoid those sensitive areas
by focusing the optimization process only on regions with highest
squared curvature value.

>>>>

We do not use similarity terms in this section, thus we postpone the definition of such terms until later in this
article, with the description of how DCE can be used in an image segmentation framework.

@@

In figure \ref{fig:m1-square-flow} we see some results for the DCE algorithm with $m=1$. We observe a global evolution
towards rounder shapes, but with several artifacts. We minimize the effects of a jaggy boundary by setting $\alpha >
0$. Nonetheless, a higher estimation ball radius creates unstable shapes. In fact, the estimator is very sensitive in
regions of low squared curvature, and it is precisely in those regions that spurious pixels are created.

@@

\subsection{A more stable model.}
In the previous section we noticed that the algorithm produces shapes with many artifacts due to the small uncertainties
of the estimator along regions of low squared curvature. We argue that, evaluating the estimation ball along outer
ring sets we avoid those sensitive areas by focusing the optimization process only on regions with highest squared
curvature value.
